---
title: "STAA57 Final Project Report "
author: "Team 10 (Daniela Venturo Esaine, Reizwan Chodhury, Ralph Samson Lal, Xiaotong Ye)"
output: html_notebook
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
## echo=FALSE stops the code chunk from appearing in the html document
## warning=FALSE / message=FALSE stop R warnings/messages from appearing in the knit document
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


***

<!-- 
(everything below in here is an .html comment)

Instructions: 
- Use typical structure of data analysis report, w/ sections:
    + Introduction
    + Data
    + Analysis
    + Summary
    + Appendix (optional)
- Report should be 5 pages MAX (when compiled/knit as pdf)
- Appendix does not count towards page limit
- Put all your data in a separate "./data/" sub-folder 
- Submit compressed project folder 
- You submissions should be reproducible (i.e. I should be able to   
  re-compile your report with a click of the Preview/Knit button) 

-->

## Introduction 

## Data 


#### DATA ANAYLSIS

=====================================================================
6. Comment on unemployment


Read Labour force survey, 2018, based to 2011 census population
```{r}

```

# Levels of Education
2: Gr 11 to 13, graduate
3: Some post secondary
4: Post secondary certificate or diploma
5: University: bachelors degree
6: University: graduate degree

```{r}
# joblessness of Unemployed individuals by education tiers
lfs_sub %>% 
  filter(lfsstat %in% 3 & educ %in% 2:6 & !is.na(durunemp)) %>% 
  mutate(educ = factor(educ)) %>%
  group_by(educ) %>% 
  select(educ, durunemp) %>% 
  mutate(durunemp_in_years = round(durunemp/52)) %>% #since Duration of unemployment in weeks
  count(durunemp_in_years) %>% 
  arrange(desc(durunemp_in_years)) %>%
  mutate(durunemp_in_years = factor(durunemp_in_years)) %>% 
  mutate(number_of_individuals = n) %>% 
  ggplot(aes(x=durunemp_in_years, y=number_of_individuals, fill = durunemp_in_years))+
  geom_bar(stat = "identity")+
  facet_wrap(facets = ~educ)+
  ggtitle("Duration of Unemployment for different Education levels")
```
Is the difference seen above statistically significant, specifically does the duration of unemployment depend on education?
```{r}
lfs_sub %>% 
  filter(lfsstat %in% 3 & educ %in% 2:6) %>% 
  mutate(educ = factor(educ)) %>% 
  independence_test( durunemp ~ educ, data = ., distribution = "approx" )
```
Conclusion: The P-value is extremely small, so there is overwhelming evidence that education affects Duration of unemployment  

Then is there a significant improvement in having a univeristy degree instead of regular Highschool education? Lets perform a TukeyTest

# Levels of Education
4: Post secondary certificate or diploma
5: University: bachelors degree
6: University: graduate degree
```{r}
lfs.aov=lfs_sub %>% 
  filter(lfsstat %in% 3 & educ %in% 4:6) %>%
  mutate(educ=factor(educ)) %>% 
  aov(durunemp ~ educ, data=.)
TukeyHSD(lfs.aov)
```
As evident from the Tukey test, Duration of unemployment in weeks is NOT vastly different from University: bachelors degree to Post secondary certificate/diploma (p>0.05).
But an University: graduate degree to Post secondary certificate/diploma has a very significant difference in duration of unemployment(p<0.05).
Also its significant to note that Duration of unemployment is significantly different between a graduate degree and a bachelors aswell.

From this we can conclude based on duration of unemployment, that is assuming that a area of education is "worth-it" given great reduction in unemployment. One should consider getting a graduates degree to greatly reduce change of unemployment. but getting a bachelors only provides a much lesser benifit in comparison to a graduates degree.

Therefore using this critera, yes a University degree is worthit Especially a Graduates Degree!!!.
=====================================================================


## Summary 


***  

## Appendix 

(*Everything here does not count towards page limit*)


