---
title: "STAA57 Final Project Report "
author: "Team 10 (Daniela Venturo Esaine, Reizwan Chodhury, Ralph Samson Lal, Xiaotong Ye)"
output: html_notebook
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
## echo=FALSE stops the code chunk from appearing in the html document
## warning=FALSE / message=FALSE stop R warnings/messages from appearing in the knit document
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(coin)
library(broom)
```


***

<!-- 
(everything below in here is an .html comment)

Instructions: 
- Use typical structure of data analysis report, w/ sections:
    + Introduction
    + Data
    + Analysis
    + Summary
    + Appendix (optional)
- Report should be 5 pages MAX (when compiled/knit as pdf)
- Appendix does not count towards page limit
- Put all your data in a separate "./data/" sub-folder 
- Submit compressed project folder 
- You submissions should be reproducible (i.e. I should be able to   
  re-compile your report with a click of the Preview/Knit button) 

-->

## Introduction 

## Data 


#### DATA ANAYLSIS

=====================================================================
6.
UNEMPLOYMENT RATE COMPARISON BETWEEN EDUCATION LEVELS IN THE LABOUR FORCE SURVEY

Considering that we wanted to focus on time-to-amortize-degree as a criterion for being "worth-it", It is obvious that one of the greatest affectors of this is employment or equivalently unemployment. Therefore we suggest Unemployment as a seconday criterion for being "worth-it", we define the criterion as follows:
"The Degree level (BSc, MSC, Highschool, College) that shows lowest level of unemployment rate is the most worth-it and would contribute to a faster amortization of degree cost".

The First part of our analysis will focus on graphically presenting unemployment rate among individuals in 6 levels of education as defined in the lfs dataset.

The Second part will run a tukey analysis to statistically prove and answer "is there a significant, unemployment rate difference among the levels of education"

Read Labour force survey, 2018, based to 2011 census population
```{r}
lfs_toronto = read_csv("data/LFS_Toronto.csv")
```

# Levels of Education
2: Gr 11 to 13, graduate
3: Some post secondary
4: Post secondary certificate or diploma
5: University: bachelors degree
6: University: graduate degree

```{r}
# joblessness of Unemployed individuals by education tiers
# lfs_toronto %>% 
#   filter(lfsstat %in% 3 & educ %in% 2:6 & !is.na(durunemp)) %>% 
#   mutate(educ = factor(educ)) %>%
#   group_by(educ) %>% 
#   select(educ, durunemp) %>% 
#   mutate(durunemp_in_years = round(durunemp/52)) %>% #since Duration of unemployment in weeks
#   count(durunemp_in_years) %>% 
#   arrange(desc(durunemp_in_years)) %>%
#   mutate(durunemp_in_years = factor(durunemp_in_years)) %>% 
#   mutate(number_of_individuals = n) %>% 
#   ggplot(aes(x=durunemp_in_years, y=number_of_individuals, fill = durunemp_in_years))+
#   geom_bar(stat = "identity")+
#   facet_wrap(facets = ~educ)+
#   ggtitle("Duration of Unemployment for different Education levels")

# lfs_toronto %>% 
#   filter(educ %in% 2:6, lfsstat == 3) %>% # lfsstat == 3  unemployed
#   mutate(educ = factor(educ)) %>% 
#   select(CASEID, educ) %>% 
#   group_by(educ) %>% 
#   count(educ) %>% 
#   transmute(individuals_unemployed = n)

(toronto_unemplrate = lfs_toronto %>% 
  summarise(UNEMPL = sum(lfsstat == 3)/sum(lfsstat!=4)) %>% pull())

lfs_toronto %>%
  filter(educ %in% 2:6) %>% # lfsstat == 3  unemployed
  mutate(educ = factor(educ)) %>% 
  group_by(educ) %>% 
  summarise(UNEMPLrate = sum(lfsstat == 3)/sum(lfsstat != 4)) %>% 
  arrange(UNEMPLrate) %>% 
  mutate(diff_from_aggregate = UNEMPLrate - toronto_unemplrate)
  
```
In the above comparison with the Toronto unemployment rate, we see educ levels 6,4 and 5 are below the Toronto unemployment rate, and educ level 2 and 3 are above it. This shows that any post secondary education is worth-it in comparison to not having a post secondar education.

But when focusing on "is university worth it", we found a surprising result, the unemployment rate for individuals with a bachelors degree is higher ever so much than one with a non-bachelors Post secondary certificate/diploma. So just based off of this result a Post secondary certificate/diploma is more worth it to that of a bachelors degree, this is even more affirmed by the fact that a Post secondary certificate/diploma cost less than a University bachelors degree meaning that the combined influence of lower cost education plus lower unemployment rate makes University not worth-it, in atleast this comparison. This result can be easily verfied for the employment rate aswell[see apendix]

But the redeeming result comes from the fact that having a University graduate degree puts an individual in the category with the lowest unemployment rate, and it is common knowlege that one needs a bachelors before moving into graduate studies. Therefore overall a University degree is indeed worth-it to not having a university Degree in regard to unemployment.









Is the difference in status of unemployment statistically significant, specifically does the status of employment/unemployment depend on education?
here we consider only lfsstat level 1 and 3. Employed-at-work and Unemployed respectively. We ignore lfsstat level 2 given they are also employed but absent from work. We focus only on the status of being unemployed vs employed.
```{r}
lfs_toronto %>% 
  filter(lfsstat %in% c(1,3) & educ %in% 2:6) %>% 
  mutate(educ = factor(educ)) %>% 
  independence_test( lfsstat ~ educ, data = ., distribution = "approx" )
```
Conclusion: The P-value is extremely small, showing that the null hypothesis of unemployment status being independent of education level is very unlikely, therefore there is overwhelming evidence that education affects unemployment.
```{r}
lfs_toronto %>% filter(lfsstat !=4 & educ %in% 2:6) %>% 
  mutate(educ = factor(educ), unempl = (lfsstat == 3)) %>% 
  ggplot(aes(x=educ, fill=unempl))+
  geom_bar(position = "fill")

# Does educ level affect unemployment significantly in any regard
lfs_toronto %>% filter(lfsstat !=4 & educ %in% 4:6) %>% 
  mutate(educ = factor(educ), unempl = factor(lfsstat == 3)) %>% 
  chisq_test(unempl ~ educ, data = .,
             distribution = "approx")

# Is there a statistically significant difference in affect on
# unemployment between educ level 5 and 6
# 5: University: bachelors degree
# 6: University: graduate degree
lfs_toronto %>% filter(lfsstat !=4 & educ %in% c(5,6)) %>% 
  mutate(educ = factor(educ), unempl = factor(lfsstat == 3)) %>% 
  chisq_test(unempl ~ educ, data = .,
             distribution = "approx")

# Is there a statistically significant difference in affect on
# unemployment between educ level 4 and 5
# 4: Post secondary certificate or diploma
# 5: University: bachelors degree
lfs_toronto %>% filter(lfsstat !=4 & educ %in% c(4,5)) %>% 
  mutate(educ = factor(educ), unempl = factor(lfsstat == 3)) %>% 
  chisq_test(unempl ~ educ, data = .,
             distribution = "approx")

# Is there a statistically significant difference in affect on
# unemployment between educ level 4 and 6
# 4: Post secondary certificate or diploma
# 6: University: graduate degree
lfs_toronto %>% filter(lfsstat !=4 & educ %in% c(4,6)) %>% 
  mutate(educ = factor(educ), unempl = factor(lfsstat == 3)) %>% 
  chisq_test(unempl ~ educ, data = .,
             distribution = "approx")
```




Then is there a significant improvement in having a univeristy degree instead of regular Highschool education? Lets perform a TukeyTest

# Levels of Education
2: Gr 11 to 13, graduate
3: Some post secondary
4: Post secondary certificate or diploma
5: University: bachelors degree
6: University: graduate degree
```{r}
lfs.aov=lfs_toronto %>%
  filter(lfsstat !=4 & educ %in% 2:6) %>% 
  mutate(educ = factor(educ), unempl = (lfsstat == 3)) %>%
  aov(flowunem ~ educ, data=.)
TukeyHSD(lfs.aov)

lfs.aov=lfs_toronto %>%
  filter(lfsstat !=4 & educ %in% 2:6) %>% 
  mutate(educ = factor(educ), empl = (lfsstat != 3)) %>%
  aov(empl ~ educ, data=.)
TukeyHSD(lfs.aov)
```
As evident from the Tukey test, Duration of unemployment in weeks is NOT vastly different from University: bachelors degree to Post secondary certificate/diploma (p>0.05).
But an University: graduate degree to Post secondary certificate/diploma has a very significant difference in duration of unemployment(p<0.05).
Also its significant to note that Duration of unemployment is significantly different between a graduate degree and a bachelors aswell.

From this we can conclude based on duration of unemployment, that is assuming that a area of education is "worth-it" given great reduction in unemployment. One should consider getting a graduates degree to greatly reduce change of unemployment. but getting a bachelors only provides a much lesser benifit in comparison to a graduates degree.

Therefore using this critera, yes a University degree is worthit Especially a Graduates Degree!!!.
=====================================================================


## Summary 


***  

## Appendix 

(*Everything here does not count towards page limit*)
EMPLOYMENT RATE COMPARISON BETWEEN EDUCATION LEVELS IN THE LABOUR FORCE SURVEY
```{r}
(toronto_emplrate = lfs_toronto %>% 
  summarise(EMPL = sum(lfsstat %in% c(1,2))/sum(lfsstat!=4)) %>% pull())

lfs_toronto %>%
  filter(educ %in% 2:6) %>% # lfsstat == 3  unemployed
  mutate(educ = factor(educ)) %>% 
  group_by(educ) %>% 
  summarise(EMPLrate = sum(lfsstat %in% c(1,2))/sum(lfsstat != 4)) %>% 
  arrange(EMPLrate) %>% 
  mutate(diff_from_aggregate = EMPLrate - toronto_emplrate)
```

