---
title: "STAA57 Final Project Report "
author: "Team 10 (Daniela Venturo Esaine, Reizwanul Karim Chowdhury, Ralph Samson Lal, Xiaotong Ye)"
output: html_notebook
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
## echo=FALSE stops the code chunk from appearing in the html document
## warning=FALSE / message=FALSE stop R warnings/messages from appearing in the knit document
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(stringr)
library(ggplot2)
```


***

<!-- 
(everything below in here is an .html comment)

Instructions: 
- Use typical structure of data analysis report, w/ sections:
    + Introduction
    + Data
    + Analysis
    + Summary
    + Appendix (optional)
- Report should be 5 pages MAX (when compiled/knit as pdf)
- Appendix does not count towards page limit
- Put all your data in a separate "./data/" sub-folder 
- Submit compressed project folder 
- You submissions should be reproducible (i.e. I should be able to   
  re-compile your report with a click of the Preview/Knit button) 

-->

## Introduction 

"Is university worth it?" is one of the hardest questions to answer. University is a very different experience from person to person depending on various factors. One of the main worries of most people is the heavy economical investment university takes. This skews the question towards the idea of measuring worth by future economical gain that cancels out the original investment. Therefore, to investigate if university is worth it, it makes sense to calculate the amount of time it takes to amortize total tuition cost in Canada.

Since tuition expenses show great variance depending on factors such as nationality, type of degree, or field of study, to have a relevant conclusion it is necessary to answer the following questions:

1. Is it worth it to get a Bachelor's degree as a Canadian domestic student compared to an international student?
2. Is it worth it to get a Masters degree as a Canadian domestic student compared to an international student?
3. Is it worth it to get a masters degree immediately after getting a bachelors degree or is it better to invest in a masters degree after a few years?
4. What is the most "worth-it" field of study? (for undergraduate and graduate, for international and domestic)
5. What is the least "worth-it" field of study? (for undergraduate and graduate, for international and domestic)
6. Who has a bigger rate of unemployment? Bachelor degrees or master degrees?

## Data 

To answer the questions stated above it is required to get the mean income for each level of study (undergraduate and graduate) from the LFS data and then use those numbers to compare them against the tuition costs from the Univcan and statcan data.

The original sources for the data are:
Tuition data:
https://www.univcan.ca/universities/facts-and-stats/tuition-fees-by-university/
Provides graduate and undergraduate data for domestic and international students.

https://www150.statcan.gc.ca/n1/en/daily-quotidien/180905/dq180905b-eng.pdf?st=KKHzDvP6
Provides graduate and undergraduate data based on field of study.

Income data:
http://sda.chass.utoronto.ca/sdaweb/html/lfs.htm
http://sda.chass.utoronto.ca/sdaweb/tmpdir/AAkQ0GVH.txt <-- codebook

#### Webscraping https://www.univcan.ca/universities/facts-and-stats/tuition-fees-by-university/
```{r}
URL = 'https://www.univcan.ca/universities/facts-and-stats/tuition-fees-by-university/'
page = read_html(url(URL))

univcan_data =   
  page %>% 
  html_nodes(xpath = '//*[@id="data_table"]') %>%
  html_table(fill = TRUE) %>% 
  as.data.frame()
univcan_data = univcan_data[-1,]
univcan_data
```

#### Setting up the data in interest
```{r}
domestic_undergraduate =
  univcan_data %>% 
  mutate(domestic_undergraduate_tuition = str_extract(Undergraduate, "(\\d+)[^-*]*$")) %>% 
  select(University, Province, domestic_undergraduate_tuition) %>% 
  filter(Province == "Ontario") %>% na.omit()
domestic_undergraduate$domestic_undergraduate_tuition =
  as.numeric(gsub(",","",domestic_undergraduate$domestic_undergraduate_tuition))
domestic_undergraduate
######################################################################################################################
international_undergraduate =
  univcan_data %>% 
  mutate(international_undergraduate_tuition = str_extract(Undergraduate.1, "(\\d+)[^-*]*$")) %>% 
  select(University, Province, international_undergraduate_tuition) %>% 
  filter(Province == "Ontario") %>% na.omit()
international_undergraduate$international_undergraduate_tuition = 
  as.numeric(gsub(",","", international_undergraduate$international_undergraduate_tuition))
international_undergraduate
######################################################################################################################
domestic_graduate =
  univcan_data %>% 
  mutate(domestic_graduate_tuition = str_extract(Graduate, "(\\d+)[^-*]*$")) %>% 
  select(University, Province, domestic_graduate_tuition) %>% 
  filter(Province == "Ontario") %>% na.omit()
domestic_graduate$domestic_graduate_tuition = 
  as.numeric(gsub(",", "", domestic_graduate$domestic_graduate_tuition))
domestic_graduate
######################################################################################################################
international_graduate =
  univcan_data %>% 
  mutate(international_graduate_tuition = str_extract(Graduate.1, "(\\d+)[^-*]*$")) %>% 
  select(University, Province, international_graduate_tuition) %>% 
  filter(Province == "Ontario") %>% na.omit()
international_graduate$international_graduate_tuition = 
  as.numeric(gsub(",","", international_graduate$international_graduate_tuition))
international_graduate
```


#### DATA ANAYLSIS

#### Q1: Get a bachelor's tuition (international vs. domestic)
```{r}
domestic_undergraduate %>% 
  arrange(domestic_undergraduate_tuition) %>% 
  ggplot(aes(x=University, y = domestic_undergraduate_tuition)) + 
  geom_point() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())

international_undergraduate %>% 
  arrange(international_undergraduate_tuition) %>% 
  ggplot(aes(x=University, y = international_undergraduate_tuition)) + 
  geom_point() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
```


#### Shows Domestic vs. International (used LEFT JOIN)
```{r}
domestic_international_undergraduate = 
  left_join(domestic_undergraduate, international_undergraduate, by = "University")

domestic_international_undergraduate %>% 
  ggplot(aes(x = University, y = Tuition, color = TypeOfStudent)) + 
  geom_point(aes(y = domestic_undergraduate_tuition, col = "Domestic")) + 
  geom_point(aes(y = international_undergraduate_tuition, col = "International")) +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
```


#### Q2: Get a masters (international vs. domestic)
```{r}
domestic_graduate %>% 
  arrange(domestic_graduate_tuition) %>% 
  ggplot(aes(x=University, y = domestic_graduate_tuition)) + 
  geom_point() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())

international_graduate %>% 
  arrange(international_graduate_tuition) %>% 
  ggplot(aes(x=University, y = international_graduate_tuition)) + 
  geom_point() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
```


#### Shows Domestic vs. International (used LEFT JOIN)
```{r}
domestic_international_graduate = 
  left_join(domestic_graduate, international_graduate, by = "University")
domestic_international_graduate %>% 
  ggplot(aes(x = University, y = Tuition, color = TypeOfStudent)) + 
  geom_point(aes(y = domestic_graduate_tuition, col = "Domestic")) + 
  geom_point(aes(y = international_graduate_tuition, col = "International")) + 
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
```