---
title: "STAA57 Final Project Report "
author: "Team 10 (Daniela Venturo Esaine, Reizwan Chodhury, Ralph Samson Lal, Xiaotong Ye)"
output: html_notebook
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
## echo=FALSE stops the code chunk from appearing in the html document
## warning=FALSE / message=FALSE stop R warnings/messages from appearing in the knit document
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(stringr)
library(ggplot2)

timeToAmortize <- function(yearEarning, tuition){
  time = (tuition*4)/yearEarning
  return(time)
}
```

***

<!-- 
(everything below in here is an .html comment)

Instructions: 
- Use typical structure of data analysis report, w/ sections:
    + Introduction
    + Data
    + Analysis
    + Summary
    + Appendix (optional)
- Report should be 5 pages MAX (when compiled/knit as pdf)
- Appendix does not count towards page limit
- Put all your data in a separate "./data/" sub-folder 
- Submit compressed project folder 
- You submissions should be reproducible (i.e. I should be able to   
  re-compile your report with a click of the Preview/Knit button) 

-->

## Introduction 

"Is university worth it?" is one of the hardest questions to answer. University is a very different experience from person to person depending on various factors. One of the main worries of most people is the heavy economical investment university requires. This skews the question towards the idea of measuring worth by future economical gain that cancels out the original investment. Therefore, to investigate if university is worth it, it makes sense to calculate the amount of time it takes to amortize total tuition cost in Canada, and factors that affect the amortization process.

Since tuition expenses show great variance depending on factors such as nationality(immigration status?), type of degree, or field of study, to have a relevant conclusion it is necessary to answer the following questions:

1. Is it worth it to get a Bachelor's degree as a Canadian domestic student compared to an international student?
2. Is it worth it to get a Masters degree as a Canadian domestic student compared to an international student?
3. What is the most "worth-it" field of study? (for undergraduate and graduate, for international and domestic)
4. What is the least "worth-it" field of study? (for undergraduate and graduate, for international and domestic)
5. Is unemployment vastly different between individuals having Non-University education and University Degree?

## Data 

To answer the questions stated above it is required to get tuition costs depending on graduate and undergraduate levels of study and fields of study. To do that we will webscrape data from univcan.ca that will let us know the average tuition for graduate and undergraduate degrees. Tables from statcan will indicate the average tuition for international and domestic students at different fields of study as well as different levels of study. Unemployment and income data will be processed from csv files obtained from census data from LFS(and CFS?). 

#### DATA ANAYLSIS

#### Q1: Get a bachelor's tuition (international vs. domestic)

#### Q2: Get a masters (international vs. domestic)

#### Q3: Most worth it field of study. (for undergraduate and graduate, for international and domestic)
```{r echo=FALSE}
# loading data sets
canUndergrad = read_csv("data/can-undergrad.csv")
canGrad = read_csv("data/can-grad.csv")
interUndergrad = read_csv("data/inter-undergrad.csv")
interGrad = read_csv("data/inter-grad.csv")
income = read_csv("data/income6.csv")

income = group_by(income, CorrespondingTo) %>% summarise(avgIncome = mean(`Average after-tax income ($)`)) %>% rename(Field_of_study = 'CorrespondingTo')

mostWorthIt <- function(dat){
  dat = dat %>% rename(y1 = '2014-2015', y2 = '2015-2016', y3 = '2016-2017', y4 = '2017-2018', y5 = '2018-2019') %>% mutate(avgTuition = (`y1` + `y2` + `y3` + `y4` + `y5`)/5) %>% right_join(income, by = "Field_of_study") %>% mutate(amortizeTime = timeToAmortize(avgIncome, avgTuition)) %>% arrange(amortizeTime) %>% head(1)
  return(dat)
}

leastWorthIt <- function(dat){
  dat = dat %>% rename(y1 = '2014-2015', y2 = '2015-2016', y3 = '2016-2017', y4 = '2017-2018', y5 = '2018-2019') %>% mutate(avgTuition = (`y1` + `y2` + `y3` + `y4` + `y5`)/5) %>% right_join(income, by = "Field_of_study") %>% mutate(amortizeTime = timeToAmortize(avgIncome, avgTuition)) %>% arrange(desc(amortizeTime)) %>% head(1)
  return(dat)
}
```

#### Q4: Least worth it field of study. (for undergraduate and graduate, for international and domestic)

To find the least worth it field of study for each category (undergraduate international or domestic and graduate international or domestic) we will be calculating the average tuition fees accross 5 years and then based on income per field of study calculate the time to amortize said tuition. The longest time will correspond to the "least worth it" field of study. 

The income will be drawn from canadian income datasets since we assume all of the categories will be working in their desired field of study in Canada. We will only be using the average employment income after tax for each field of study.

Time in Year?Months?

Least worth it field for Canadian Undergraduate:
```{r}
leastWorthIt(canUndergrad)
```

Least worth it field for International Undergraduate:
```{r}
leastWorthIt(interUndergrad)
```

Least worth it field for Canadian Graduate:
```{r}
leastWorthIt(canGrad)
```

Least worth it field for International Graduate:
```{r}
leastWorthIt(interGrad)
```

#### Q5: Comment on unemployment

## Summary 

Based on the results from question 1 and 2, it is safe to conclude that International student tuition for any degree is higher than Domestic student tuition. However, the gap between tuition is lessened when going from a bachelor's degree to a masters degree. This means it is easier to pay off a masters than a bachelors degree as an international student. Domestic student tuition fees are generally lower. In the end, both are worth it.

Based on the results of q4 the least worth it field of study for Canadian Undergraduates is Dentistry as it takes the longest to pay off tuition. The least worth it for International Undergraduate is Visual and performing arts, and communications technologies. For Canadian and International Graduate the least worth it field is Business, management and public administration. However, by no means does this imply it is not worth it. Education is an investment, the statistics calculated just implies it is harder to get a good payout from that field.

==can be replaced by conclusion in q5==
(To comment on unemployment, the degree of your study does affect greatly on the chances of being unemployed as the difference in the duration of unemployment is very significant between the two. Therefore it is recommendable to get a masters degree.) 


***  

## Appendix 

(*Everything here does not count towards page limit*)


