---
title: "STAA57 Final Project Report "
author: "Team 10 (Daniela Venturo Esaine, Reizwan Chodhury, Ralph Samson Lal, Xiaotong Ye)"
output: html_notebook
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
## echo=FALSE stops the code chunk from appearing in the html document
## warning=FALSE / message=FALSE stop R warnings/messages from appearing in the knit document
library(tidyverse)
```


***

<!-- 
(everything below in here is an .html comment)

Instructions: 
- Use typical structure of data analysis report, w/ sections:
    + Introduction
    + Data
    + Analysis
    + Summary
    + Appendix (optional)
- Report should be 5 pages MAX (when compiled/knit as pdf)
- Appendix does not count towards page limit
- Put all your data in a separate "./data/" sub-folder 
- Submit compressed project folder 
- You submissions should be reproducible (i.e. I should be able to   
  re-compile your report with a click of the Preview/Knit button) 

-->

## Introduction 

(*Description of questions that are being investigated*)

## Data 

(*Description of data used to answer the questions*)

## Analysis 

(*Main body of analysis, containing data summaries (tables/plots),  statistical analyses (estimations, tests), and modelling (regression, classification) *)

### Some Subsection Title

<!-- You can organize content in subsections -->

(*Plots should be created in R, and not imported from file*)

```{r, echo = FALSE, fig.width = 5, fig.heigh = 5}
tibble( t = seq(0, 2*pi, by=0.1) ) %>% 
  mutate( x = 16*sin(t)^3, 
          y = 13*cos(t)-5*cos(2*t)-2*cos(3*t)-cos(4*t) ) %>% 
  ggplot(aes( x = x, y = y)) + 
  geom_polygon( fill = "pink") +
  coord_fixed() 
```

#### Some Subsubsection Title

(*R output tables can be converted to .html with* `knitr::kable()`) 

```{r, echo = FALSE}
tibble( X = c("this", "is"), 
        Y = c("my", "table") ) %>% 
  knitr::kable()
```
<!-- 
for more help on RMarkdown see: https://rmarkdown.rstudio.com/lesson-15.html 
-->


## Summary 

(*Recap of your findings and conclusions*)



***  

## Appendix 

(*Everything here does not count towards page limit*)


