---
title: "STAA57 Final Project Report "
author: "Team 10 (Daniela Venturo Esaine, Reizwan Chodhury, Ralph Samson Lal, Xiaotong Ye)"
output: html_notebook
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
## echo=FALSE stops the code chunk from appearing in the html document
## warning=FALSE / message=FALSE stop R warnings/messages from appearing in the knit document
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(stringr)
library(ggplot2)
```


***

<!-- 
(everything below in here is an .html comment)

Instructions: 
- Use typical structure of data analysis report, w/ sections:
    + Introduction
    + Data
    + Analysis
    + Summary
    + Appendix (optional)
- Report should be 5 pages MAX (when compiled/knit as pdf)
- Appendix does not count towards page limit
- Put all your data in a separate "./data/" sub-folder 
- Submit compressed project folder 
- You submissions should be reproducible (i.e. I should be able to   
  re-compile your report with a click of the Preview/Knit button) 

-->

## Introduction 

"Is university worth it?" is one of the hardest questions to answer. University is a very different experience from person to person depending on various factors. One of the main worries of most people is the heavy economical investment university takes. This skews the question towards the idea of measuring worth by future economical gain that cancels out the original investment. Therefore, to investigate if university is worth it, it makes sense to calculate the amount of time it takes to amortize total tuition cost in Canada.

Since tuition expenses show great variance depending on factors such as nationality, type of degree, or field of study, to have a relevant conclusion it is necessary to answer the following questions:

1. Is it worth it to get a Bachelor's degree as a Canadian domestic student compared to an international student?
2. Is it worth it to get a Masters degree as a Canadian domestic student compared to an international student?
3. Is it worth it to get a masters degree immediately after getting a bachelors degree or is it better to invest in a masters degree after a few years?
4. What is the most "worth-it" field of study? (for undergraduate and graduate, for international and domestic)
5. What is the least "worth-it" field of study? (for undergraduate and graduate, for international and domestic)
6. Who has a bigger rate of unemployment? Bachelor degrees or master degrees?

## Data 

To answer the questions stated above it is required to get the mean income for each level of study (undergraduate and graduate) from the LFS data and then use those numbers to compare them against the tuition costs from the Univcan and statcan data.

The original sources for the data are:
Tuition data:
https://www.univcan.ca/universities/facts-and-stats/tuition-fees-by-university/
Provides graduate and undergraduate data for domestic and international students.

https://www150.statcan.gc.ca/n1/en/daily-quotidien/180905/dq180905b-eng.pdf?st=KKHzDvP6
Provides graduate and undergraduate data based on field of study.

Income data:
http://sda.chass.utoronto.ca/sdaweb/html/lfs.htm
http://sda.chass.utoronto.ca/sdaweb/tmpdir/AAkQ0GVH.txt <-- codebook

#### Webscraping https://www.univcan.ca/universities/facts-and-stats/tuition-fees-by-university/


#### Setting up the data in interest



#### DATA ANAYLSIS

#### Q1: Get a bachelor's tuition (international vs. domestic)



#### Shows Domestic vs. International (used LEFT JOIN)



#### Q2: Get a masters (international vs. domestic)



#### Shows Domestic vs. International (used LEFT JOIN)





#### Q4: Most worth it field of study. (for undergraduate and graduate, for international and domestic)

The data we use is come from that link:
https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/dt-td/Rp-eng.cfm?TABID=2&LANG=E&A=R&APATH=3&DETAIL=0&DIM=0&FL=A&FREE=0&GC=35&GL=-1&GID=1341685&GK=1&GRP=1&O=D&PID=111839&PRID=10&PTYPE=109445&S=0&SHOWALL=0&SUB=0&Temporal=2017&THEME=123&VID=0&VNAMEE=&VNAMEF=&D1=0&D2=0&D3=0&D4=0&D5=0&D6=0&fbclid=IwAR2UiD5ZcCwmoBu9g7ZeIkvZwQD3H1uIJvWYusU7zu0seh9wjdY89H0kjFo
undergrduate:
```{r}
income_new = read.csv("../data/Is-University-Worth-It/incomeNew.csv")
income_new
```


In this question, we created two functions to find the least time to ammortize based on income and tuition fees for different fields of study in graduate and undergraduate students in general. Inside this function, we also implemented a new sub function to represent the time to ammortize for graduate and undergraduate students. After we applied this function into the data frame of tuition fees for domestic undergraduate, domestic graduate, international undergraduate, and international graduate. The way we evaluate the most worth field of study is based on the least time to ammortize, that is, the time to pay all of the tuition fees back if he/she find the job immediately.

For undergraduate students(for both domestic and international), education study is the most worth field of study. So it is better to invest study in education during studying in undergraduate school. For graduate domestic students, law is the most worth field of study. Finally, for graduate international students, dentistry is the most worth field of study. By looking from their income, thos field of study are always have very high average income.
```{r}
Avg_income = income %>% arrange(desc(avgIncome))
Avg_income
#ggplot(aes(x = Major.field.of.study...Classification.of.Instructional.Programs..CIP..2016..43., y = Average.employment.income.... ), data = income)+geom_bar(stat = "identity")
#ggplot(aes(x = Major.field.of.study...Classification.of.Instructional.Programs..CIP..2016..43., y = Average.employment.income....), data = income)+geom_bar()
```
```{r}
timeToAmortizeUnder <- function(yearEarning, tuition){
  time = (tuition*4)/yearEarning
  return(time)
}
timeToAmortizeGrad <- function(yearEarning, tuition){
  time = (tuition*2)/yearEarning
  return(time)
}
income = group_by(income_new, CorrespondingTo) %>% summarise(avgIncome = mean(`Average.after.tax.income....`)) %>% rename(Field_of_study = 'CorrespondingTo')
can_under = read_csv("../data/Is-University-Worth-It/can-undergrad.csv")
can_grad = read_csv("../data/Is-University-Worth-It/can-grad.csv")
inter_under = read_csv("../data/Is-University-Worth-It/inter-undergrad.csv")
inter_grad = read_csv("../data/Is-University-Worth-It/inter-grad.csv")
mostWorthItUnder <- function(dat){
  dat = dat %>% rename(y1 = '2014-2015', y2 = '2015-2016', y3 = '2016-2017', y4 = '2017-2018', y5 = '2018-2019') %>% mutate(avgTuition = (`y1` + `y2` + `y3` + `y4` + `y5`)/5) %>% right_join(income, by = "Field_of_study") %>% mutate(amortizeTime = timeToAmortizeUnder(avgIncome, avgTuition)) %>% arrange(amortizeTime) %>% head(1)
  return(dat)
}
mostWorthItGrad <- function(dat){
  dat = dat %>% rename(y1 = '2014-2015', y2 = '2015-2016', y3 = '2016-2017', y4 = '2017-2018', y5 = '2018-2019') %>% mutate(avgTuition = (`y1` + `y2` + `y3` + `y4` + `y5`)/5) %>% right_join(income, by = "Field_of_study") %>% mutate(amortizeTime = timeToAmortizeGrad(avgIncome, avgTuition)) %>% arrange(amortizeTime) %>% head(1)
  return(dat)
}
mostWorthItUnder(can_under)
mostWorthItGrad(can_grad)
mostWorthItUnder(inter_under)
mostWorthItGrad(inter_grad)
can_under %>% arrange(desc(`2018-2019`))
```
Tuition fees in fields of study: http://odesi1.scholarsportal.info/documentation/TLAC/2017-2018/Tables_1-7_2017-2018_final.xlsx
$$This link contains of all tuition fees informations include graduate and undergraduate study for both domestic and international students. However, this data needs to be cleaned. For each of field of study, there is lower and upper value for tuition fees, we have to find the mean value between them so we can find the exactly the value of tuition fees for this field of study.$$
5. Least worth it field of study. (for undergraduate and graduate, for international and domestic)


In this question, we created two functions to find the least time to ammortize based on income and tuition fees for different fields of study in graduate and undergraduate students in general. Inside this function, we also implemented a new sub function to represent the time to ammortize for graduate and undergraduate students. After we applied this function into the data frame of tuition fees for domestic undergraduate, domestic graduate, international undergraduate, and international graduate. The way we evaluate the most worth field of study is based on the most time to ammortize, that is, the time to pay all of the tuition fees back if he/she find the job immediately.

Surprisingly, for domestic undergraduate students, Dentistry is the least worth of study since it has highest tuition for them. For domestic graduate students, Business, management and public administration is the least worth of study. For international undergraduate students, visual and performing arts, and communications technologies is the least worth of study since it has lowest average income. For international graduate students, Business, management and public administration is the least worth of study, which is same as domestic graduate students. Seems like it is not worth it to study business in graduate school. 
```{r}

Avg_income_new = income %>% arrange(avgIncome)
Avg_income_new
LeastWorthItUnder <- function(dat){
  dat = dat %>% rename(y1 = '2014-2015', y2 = '2015-2016', y3 = '2016-2017', y4 = '2017-2018', y5 = '2018-2019') %>% mutate(avgTuition = (`y1` + `y2` + `y3` + `y4` + `y5`)/5) %>% right_join(income, by = "Field_of_study") %>% mutate(amortizeTime = timeToAmortizeUnder(avgIncome, avgTuition)) %>% arrange(desc(amortizeTime) )%>% head(1)
  return(dat)
}
LeastWorthItGrad <- function(dat){
  dat = dat %>% rename(y1 = '2014-2015', y2 = '2015-2016', y3 = '2016-2017', y4 = '2017-2018', y5 = '2018-2019') %>% mutate(avgTuition = (`y1` + `y2` + `y3` + `y4` + `y5`)/5) %>% right_join(income, by = "Field_of_study") %>% mutate(amortizeTime = timeToAmortizeGrad(avgIncome, avgTuition)) %>% arrange(desc(amortizeTime) )%>% head(1)
  return(dat)
}
LeastWorthItUnder(can_under)
LeastWorthItGrad(can_grad)
LeastWorthItUnder(inter_under)
LeastWorthItGrad(inter_grad)
```
6. Comment on unemployment



## Summary 

(*Recap of your findings and conclusions*)



***  

## Appendix 

(*Everything here does not count towards page limit*)


