---
title: "Analysis_for_DraftReport"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(stringr)
```

#### Webscraping https://www.univcan.ca/universities/facts-and-stats/tuition-fees-by-university/
```{r}
URL = 'https://www.univcan.ca/universities/facts-and-stats/tuition-fees-by-university/'
page = read_html(url(URL))
univcan_data =   
  page %>% 
  html_nodes(xpath = '//*[@id="data_table"]') %>%
  html_table(fill = TRUE) %>% 
  as.data.frame()
univcan_data = univcan_data[-1,]
univcan_data
```

#### Setting up the data in interest
```{r}
domestic_undergraduate =
  univcan_data %>% 
  mutate(domestic_undergraduate_tuition = str_extract(Undergraduate, "(\\d+)[^-*]*$")) %>% 
  select(domestic_undergraduate_tuition) %>% na.omit()
domestic_undergraduate$domestic_undergraduate_tuition =
  as.numeric(gsub(",","",domestic_undergraduate$domestic_undergraduate_tuition))
domestic_undergraduate
do = domestic_undergraduate %>% mutate(sum = n()-1)
do
######################################################################################################################
international_undergraduate =
  univcan_data %>% 
  mutate(international_undergraduate_tuition = str_extract(Undergraduate.1, "(\\d+)[^-*]*$")) %>% 
  select(international_undergraduate_tuition) %>% na.omit()
international_undergraduate$international_undergraduate_tuition = 
  as.numeric(gsub(",","", international_undergraduate$international_undergraduate_tuition))
international_undergraduate
inter = international_undergraduate %>% mutate(sum = n())
inter
######################################################################################################################
domestic_graduate =
  univcan_data %>% 
  mutate(domestic_graduate_tuition = str_extract(Graduate, "(\\d+)[^-*]*$")) %>% 
  select(domestic_graduate_tuition) %>% na.omit()
domestic_graduate$domestic_graduate_tuition = 
  as.numeric(gsub(",", "", domestic_graduate$domestic_graduate_tuition))
domestic_graduate
dog = domestic_graduate %>% mutate(sum = n()+17)
dog
######################################################################################################################
international_graduate =
  univcan_data %>% 
  mutate(international_graduate_tuition = str_extract(Graduate.1, "(\\d+)[^-*]*$")) %>% 
  select(international_graduate_tuition) %>% na.omit()
international_graduate$international_graduate_tuition = 
  as.numeric(gsub(",","", international_graduate$international_graduate_tuition))
international_graduate
interg = international_graduate %>% mutate(sum = n()+18)
interg
```
#### DATA ANAYLSIS
#### Q1: Get a bachelor's tuition (international vs. domestic)



#### Q2: Get a masters (international vs. domestic)
3. Get a masters immediately after a bachelor's vs. after a few years

Assume there is four years of undergraduate study and 2 years of graduate study. The table shown below represents the total tuition fees for a domestic student and an international student have to pay if he/she is deciding to complete a master degree.
```{r}
domestic_sum = left_join(do, dog, by = "sum") %>% mutate(sum_tuition = 4*domestic_undergraduate_tuition + 2*domestic_graduate_tuition) %>% select(sum_tuition)
domestic_sum
international_sum = left_join(inter, interg, by = "sum") %>% mutate(sum_tuition = 4*international_undergraduate_tuition + 2*international_graduate_tuition) %>% select(sum_tuition)
international_sum

```

To find the proportion of a student who study for master immediately vs the proportion of a student who study for master after few years. We filtered the student who took school recently after getting the bachelor degree. We also filtered the student who does not took school recently after getting the bachelor degree. After we summarised people who get bachelor degree and use each group of people(who is taking master recently and not)divide by all bachelor degree students. We find out that people who take master immediately after he/she has got the bachelor degree is just around 8%, on the other hand, people is still not take the master yet after got the bachelor degree is almost 92%.
```{r}
ngs = read.csv("../data/ngs.csv")
data = ngs %>% select(edbefor, lf_q01)
master_immediate = data %>% filter(lf_q01 == 1 ) %>% filter(edbefor == 5) %>% summarise(num = n())
master_immediate
master_not_imme =  data %>% filter(lf_q01 == 2 ) %>% filter(edbefor == 5) %>% summarise(num = n())
master_not_imme
sum_master = master_immediate %>% pull() + master_not_imme %>% pull()
pro_masteri = master_immediate/sum_master
pro_masteri
pro_masterno = master_not_imme/sum_master
pro_masterno
```

4. Most worth it field of study. (for undergraduate and graduate, for international and domestic)
undergrduate:
domestic:
```{r}
income = read.csv("../data/income3.CSV")
```
international:
```{r}

```
graduate:
domestic:
```{r}

```
international:
```{r}

```
5. Least worth it field of study. (for undergraduate and graduate, for international and domestic)
6. Comment on unemployment
